Fast sparse period estimation

### 2014-03-31 paper.tex
added new data minor

\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{pgfplots}

@@

    \begin{axis}[name=plot1,font=\footnotesize,xmode=log,ymax=4e-1,ymode=log,height=10cm,width=9cm,xlabel={$\sigma^2$},ylabel={MSE},ylabel style={at={(0.19,0.24)}},xlabel style={at={(0.5,0.14)}}, legend style={at={(1.1,1.02)}, anchor=south,legend columns=7, cells={anchor=west,/tikz/every even column/.append style={column sep=0.2cm}}}]

@@

       \addplot[mark=x,only marks,color=black,mark options={solid,fill=black,scale=1}] table {code/data/NormalisedSamplingLLSN30geom1}; 

@@

       \addplot[mark=x,only marks,color=black,mark options={solid,fill=black,scale=1}] table {code/data/NormalisedSamplingLLSN1200geom1};

@@

     \node[rotate=17,font=\footnotesize] at (axis cs:6e-4,9e-8) {$N=30$};

@@

 \begin{axis}[name=plot2,at={(11,0)},ymax=4e-1,font=\footnotesize,xmode=log,ymode=log,height=10cm,width=9cm,xlabel={$\sigma^2$},ylabel={MSE},ylabel style={at={(0.19,0.23)}},xlabel style={at={(0.5,0.14)}}]

@@

       \addplot[mark=x,only marks,color=black,mark options={solid,fill=black,scale=1}] table {code/data/NormalisedSamplingLLSN30geom10}; 

@@

       \addplot[mark=x,only marks,color=black,mark options={solid,fill=black,scale=1}] table {code/data/NormalisedSamplingLLSN1200geom10};

@@

This section presents the results of Monte-Carlo simulations with the periodogram estimator~\cite{Haohuan2013435,Fogel1989_bit_synch_zero_crossings}, the normalised least squares estimator~\cite{Clarkson2007,McKilliam2007,Quinn_sparse_noisy_SSP_2012}, Clarkson's modification of the separable least squares line search (SLS2-new) estimator~\cite{Clarkson2007,Sidiropoulos2005}, and the quantised periodogram estimator from Section~\ref{sec:quant-peri}.  The grid distance $D$ used for the modified least squares, periodogram, and SLS2-new estimators is given by~\eqref{eq:gridwidthrecommended}.  The quantised periodogram estimator is computed using a single fast Fourier transform of length $M = 2L = 2(\ellmax - \ellmin + 1)$.  Both the periodogram and quanitised periodogram estimators use the Newton-Raphson method.  In all simulations the noise variables $w_1,\dots,w_N$ are independent and identically normally distributed with variance $\sigma^2$.  The integers $s_1,\dots,s_N$ are generated so that $s_1$ and $s_{n+1} - s_n$ for $n=2,\dots,N$ are independent and identically geometrically distributed starting from zero with means $\mu=1$ and $10$.  The true period is $T_0 = \pi/3$, the true phase is $\theta_0 = 0.2$, and $T_{\text{min}} = 0.8$ and $T_{\text{max}} = 1.5$.

>>>>

\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{pgfplots}
\pgfplotsset{compat=1.8}

@@

    \begin{axis}[name=plot1,font=\footnotesize,xmode=log,ymax=4e-1,ymode=log,height=10cm,width=9cm,xlabel={$\sigma^2$},ylabel={MSE},ylabel style={at={(0.06,0.24)}},xlabel style={at={(0.5,0.07)}}, legend style={at={(1.1,1.02)}, anchor=south,legend columns=7, cells={anchor=west,/tikz/every even column/.append style={column sep=0.2cm}}}]

@@

       \addplot[mark=x,only marks,color=black,mark options={solid,fill=black,scale=1.2}] table {code/data/NormalisedSamplingLLSN30geom1}; 

@@

       \addplot[mark=x,only marks,color=black,mark options={solid,fill=black,scale=1.2}] table {code/data/NormalisedSamplingLLSNsamp101200geom1};

@@

     \node[rotate=17,font=\footnotesize] at (axis cs:6e-4,1e-7) {$N=30$};

@@

 \begin{axis}[name=plot2,at={(11,0)},ymax=4e-1,font=\footnotesize,xmode=log,ymode=log,height=10cm,width=9cm,xlabel={$\sigma^2$},ylabel={MSE},ylabel style={at={(0.06,0.23)}},xlabel style={at={(0.5,0.07)}}]

@@

       \addplot[mark=x,only marks,color=black,mark options={solid,fill=black,scale=1.2}] table {code/data/NormalisedSamplingLLSN30geom10}; 

@@

       \addplot[mark=x,only marks,color=black,mark options={solid,fill=black,scale=1.2}] table {code/data/NormalisedSamplingLLSN1200geom10};

@@

This section presents the results of Monte-Carlo simulations with the periodogram estimator~\cite{Haohuan2013435,Fogel1989_bit_synch_zero_crossings}, the modified least squares estimator~\cite{Clarkson2007,McKilliam2007,Quinn_sparse_noisy_SSP_2012}, Clarkson's modification of the separable least squares line search (SLS2-new) estimator~\cite{Clarkson2007,Sidiropoulos2005}, and the quantised periodogram estimator from Section~\ref{sec:quant-peri}.  The grid distance $D$ used for the periodogram and SLS2-new estimators is given by~\eqref{eq:gridwidthrecommended}.  The modified least squares estimator requires a finer grid to work accurately and we choose~\eqref{eq:gridwidthrecommended} divided by three in our simulations.  The quantised periodogram estimator is computed using a single fast Fourier transform of length $M = 2L = 2(\ellmax - \ellmin + 1)$.  Both the periodogram and quanitised periodogram estimators use the Newton-Raphson method.  In all simulations the noise variables $w_1,\dots,w_N$ are independent and identically normally distributed with variance $\sigma^2$.  The integers $s_1,\dots,s_N$ are generated so that $s_1$ and $s_{n+1} - s_n$ for $n=2,\dots,N$ are independent and identically geometrically distributed starting from zero with means $\mu=1$ and $10$.  The true period is $T_0 = \pi/3$, the true phase is $\theta_0 = 0.2$, and $T_{\text{min}} = 0.8$ and $T_{\text{max}} = 1.5$.
